---
title: "Exam_questions"
author: "Your Name Here"
date: "`r Sys.Date()`"
output: html_document
---

# Short questions

Read the questions and choose an answer or write a code. When you're done,
click the "Knit" button on top of this window. You will create an .html
file, which will contain your answers.

## TIDY DATA

1. How do you define a tidy dataset?

    a) columns and rows are named and there is no data missing
    b) each column is a variable, each row is an observation
    c) each row is a variable, each column is an observation
   
2. Why is it useful to organize data in such a way?

3. Which of the following functions are used to _restructure_ a dataset?
(this often means making a tidy dataset)

    a) `summarise`, `filter`, `select`
    b) `pivot_wider`, `pivot_longer`, `separate`
    c) `lm`, `sqrt`, `table`

## DATA EXPLORATION

1. Which of the following functions are used to _transform_ a dataset? (i.e.,
explore it, pick values you want, summarize, etc.)

    a) `summarise`, `filter`, `select`
    b) `pivot_wider`, `pivot_longer`, `separate`
    c) `lm`, `sqrt`, `table`

2. You have a dataset:

```{r q1}
# install.packages("nycflights13")
library(nycflights13)
library(tidyverse)

data("flights")

flights
```

Write a short code that would find:

    a) flights that arrived more than two hours late, but didn’t leave late
    b) the most delayed flights.

3. What does this code do?

```{r q2}
flights %>%
	filter(!is.na(dep_delay), !is.na(arr_delay)) %>%
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0])
  )
```

## DATA VISUALIZATION

1. You have data that shows various types of cars and their features, `mpg`.
How would you create a histogram of `class` of the cars in the dataset?
Fill in the blanks in the code below:

```{r q3}
data("mpg")

ggplot(mpg, aes(class)) + geom_...(...)
```

2. Now, modify the above code to _fill_ the bars with colors according to
the type of drive train (`drv`).

3. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
For each of these chart types, provide one example of data that you could
visualize with it.

## ANALYSIS

1. Modify below code to run linear regression analysis for outcome flipper length with using predictors sex and body mass by using variables from palmerpenguins::penguins dataset

```{r}
# install.packages(palmerpenguins) 
palmerpenguins::penguins %>%
  lm(flipper_length_mm ~ sex + body_mass_g)
```

2. Briefly explain what below code does by commenting on each line:

```{r}
palmerpenguins::penguins %>%
  filter(year == 2007) %>%
  aov(bill_depth_mm ~ species, data = .) %>% 
  broom::tidy()
```

