---
title: "Exam_questions"
author: "Kristine"
date: "`23.09.2021`"
output: html_document
---

# Short questions

Read the questions and choose an answer or write a code. When you're done,
click the "Knit" button on top of this window. You will create an .html
file, which will contain your answers.

## TIDY DATA

1. How do you define a tidy dataset?

    
    b) each column is a variable, each row is an observation
  
   
2. Why is it useful to organize data in such a way?

it dgkjdklghsklfhskldhf

3. Which of the following functions are used to _restructure_ a dataset?
(this often means making a tidy dataset)

    
    b) `pivot_wider`, `pivot_longer`, `separate`
    

## DATA EXPLORATION

1. Which of the following functions are used to _transform_ a dataset? (i.e.,
explore it, pick values you want, summarize, etc.)

    a) `summarise`, `filter`, `select`
  

2. You have a dataset:

```{r q1}
# install.packages("nycflights13")
library(nycflights13)
library(tidyverse)

data("flights")

flights
```

Write a short code that would find:

    a) flights that arrived more than two hours late, but didn’t leave late
```{r}
Delayedflights<-
  flights%>%
  filter(dep_delay<=0 & arr_delay>120)
Delayedflights
```
    
    
    b) the most delayed flights.
    
```{r}
mostdelayedflights<-
  flights%>%
  arrange(desc(dep_delay))
mostdelayedflights
  
```
    

3. What does this code do?

```{r q2}
flights %>% #this command selects the dataset "flights", and then
	filter(!is.na(dep_delay), !is.na(arr_delay)) %>%
  #this command excludes the flights with missing (non available) values from dep_Delay and arr_delay, and then
  group_by(year, month, day) %>% 
  #groups the remaining data by year, month and day, and then
  summarise( #creates a new data frame
    avg_delay1 = mean(arr_delay), #calculating the average of arr_delay and assigning the values to the variable avg_delay1
    avg_delay2 = mean(arr_delay[arr_delay > 0]) #calculating the average of all flights that were actually delayed and assigning it to the variable avg_delay2
    
  )
```

## DATA VISUALIZATION

1. You have data that shows various types of cars and their features, `mpg`.
How would you create a histogram of `class` of the cars in the dataset?
Fill in the blanks in the code below:

```{r q3}
data("mpg")

ggplot(mpg, aes(class)) + geom_bar()
#could not create a histogram because the variables on teh x axis are not continous
```


2. Now, modify the above code to _fill_ the bars with colors according to
the type of drive train (`drv`).

```{r}
data("mpg")
ggplot(mpg, aes(class)) +
  geom_bar(aes(fill=drv)) 
  
  

```


3. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
For each of these chart types, provide one example of data that you could
visualize with it.

For line chart: geom_line - evolution 
For box plot: geom_boxplot - distribution of numeric variables 
For histogram_ geom_histogram - can be used to represent 
For area chart: geom_area - jjkfsdk
## ANALYSIS

1. Modify below code to run linear regression analysis for outcome flipper length with using predictors sex and body mass by using variables from palmerpenguins::penguins dataset

```{r}
#install.packages("palmerpenguins") 
palmerpenguins::penguins %>% 
  lm(flipper_length_mm ~ sex + body_mass_g, data=.)

```

2. Briefly explain what below code does by commenting on each line:

```{r}
palmerpenguins::penguins %>% #it selects the dataset called "penguins" from the packacke called "palmerpenguins"
  filter(year == 2007) %>% #it extracts only the data from 2007
  aov(bill_depth_mm ~ species, data = .) %>% #it runs anova analysis comparing differences between bill_depths_mm among species using the data from the previous pipe.
  broom::tidy() #it takes the tidy function from the broom package which display the results in a table.
```

