---
title: "Codebook_exam_Kristine"
author: Kristine
date: 07.10.2021
output: html_document
---
Before starting I need to load the packages "tidyverse" and "here" to be able to use the here() function before tidying the data
```{r}
library(tidyverse)
library(here)
here()
```

Now i import the dataset into environment as well as assigning it to "Covid_data" to be able to view it and work with it in the Rmarkdown file.
```{r}
covid_data <- read_delim(here("Data", "exam_data.txt"))
covid_data
```
Now we should tidy the data

Here I try to separate the first column into two subcaterogies based on the separation sign "_"
```{r}
covid_data <-
  covid_data %>% 
  separate(col = subject,
           into = c ("PatientID", "Patient_Name"),
           extra = "merge",
           sep = "-")
covid_data
```
Now I try and clean the data more and rename it to track the changes in the environment for a nice overview and removing duplicates så that we end up with 16 variables instead of 17
```{r}
clean_covid <-
  covid_data[!duplicated(as.list(covid_data))]
clean_covid
```

Now I want to rename the column that has a space instead of _

```{r}
clean_covid<-
  clean_covid %>% 
  rename(pan_day="pan day")
clean_covid
```
Now I want to change the columns age_gender because they are redundant. Separating age and gender

```{r}
clean_covid <-
  clean_covid %>% 
  pivot_longer(names_to = "gender", values_to = "age", cols=15:16)  
clean_covid
```
Now I remove the NA´s and rename the gender variables as F and M. Because the NA´s in the respective columns are just the opposite gender
```{r}
clean_covid <-
  clean_covid %>% 
  drop_na(age) %>% 
  mutate(Gender = if_else(gender == "age_female", "F", "M"))
clean_covid
 
```
Now the dataset is tidy and I can explore it

i install the packages needed for exploring

```{r}
install.packages(c("finalfit", "skimr", "naniar"))
library(finalfit)
```

Using glimpse
```{r}
finalfit::ff_glimpse(clean_covid)
```
Missing variables
In ct_results, the missing values are 209 (numerical variable type)
In payor_group, the missing values are 7087 (categorical variable type)
In patient_class, the missing values are 7077 (categorical variable type)

Checking for outliers in summary statistics

```{r}
summary(clean_covid)
```

The following categories indicated singificant outliers:

Age
rec_ver_tat
col_rec_tat


I want to show the distribution of age
```{r}
  clean_covid %>% 
  ggplot(aes(y=age))+
  geom_boxplot()
```
And the same for col_rec_tat and adding log for a nicer overview
```{r}
  clean_covid %>% 
  ggplot(aes(y=log(col_rec_tat)))+
  geom_boxplot()
```
And the same for rec_ver_tat

It doesnt look like significant outliers here by this box plot
removing log and then the top value looks like an outlier. negative values doesnt allow for log

```{r}
  clean_covid %>% 
  ggplot(aes(y=(rec_ver_tat)))+
  geom_boxplot()
```

Now we want to check if the time spent waiting for the test result improve during the 100 days

```{r}
clean_covid %>% 
  ggplot(aes(pan_day,rec_ver_tat))+
  geom_point()+
  geom_smooth(method = "lm")+
  ggpubr::stat_cor()
```

Regression analysis and scatter plot didnt reveal any significant improvement in waiting time during the 100 days. p=0.12

Checking if the chances of getting a positive test increase with the muber of tests taken
number of entries for each patient ID:
```{r}
clean_covid %>% 
  group_by(PatientID) %>% 
  tally()
```

