---
title: "Codebook_exam_Kristine"
author: Kristine
date: 07.10.2021
output: html_document
---
Before starting I need to load the packages "tidyverse" and "here" to be able to use the here() function before tidying the data
```{r}
library(tidyverse)
library(here)
here()
```

Now i import the dataset into environment as well as assigning it to "Covid_data" to be able to view it and work with it in the Rmarkdown file.
```{r}
covid_data <- read_delim(here("Data", "exam_data.txt"))
covid_data
```
Now we should tidy the data

Here I try to separate the first column into two subcaterogies based on the separation sign "_"
```{r}
covid_data <-
  covid_data %>% 
  separate(col = subject,
           into = c ("PatientID", "Patient_Name"),
           extra = "merge",
           sep = "-")
covid_data
```
Now I try and clean the data more and rename it to track the changes in the environment for a nice overview
removing duplicates
```{r}
clean_covid <-
  clean_covid[!duplicated(as.list(covid_data))]
```


